Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-08-04 xrb2/paper.tex
Added speed plots to xrb2

\newcommand{\omegadot}{\dot{\omega}}

@@

>>>>

\newcommand{\omegadot}{\dot{\omega}}
\newcommand{\enucdot}{\dot{e}_{nuc}}

@@

\begin{figure}[t]
	\centering
	\plottwo{speeds_1_100th_max.pdf}{speeds_1_1000th_max.pdf}
	\caption{Plots of flame front position vs.\ time for the 500 Hz and 1000 Hz runs. The left-hand plot shows the results when tracking the $\frac{1}{100} \max[\enucdot]$ contour, while the right-hand plot shows the results for the $\frac{1}{1000} \max[\enucdot]$ contour.}
\end{figure}
